Approximation as Differentiation: Notes

### 2025-05-25 main/category-of-families.tex
Cleanup.

Following the CHAD approach, automatic differentiation for first-order programs can also be recovered in this
setup, via the total category $\Fam(\FinVect)$. We recapitulate the basic idea here. For flat manifolds like
$\RR^n$, the tangent space and cotangent space at a point $x$ are both canonically isomorphic to $\RR^n$, so
the forward and backward derivatives at $x$ of a differentiable function $f: \RR^m \to \RR^n$ have the
following form.

@@

\subsubsection{Chain rule}

@@

\subsubsection{Forward mode automatic differentiation}

>>>>

Following the CHAD approach, automatic differentiation for first-order programs can also be recovered in this
setup, via the total category $\Fam(\FinVect)$. We recapitulate the basic idea here. For flat manifolds like
$\RR^n$, the tangent space and cotangent space at a point $x$ are both canonically isomorphic to $\RR^n$, so
the forward and backward derivatives of a differentiable function $f: \RR^m \to \RR^n$ at a point $x$ have the
following form:

@@

\subsubsection{Chain Rule}

@@

\subsubsection{Forward-Mode Automatic Differentiation}
